Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-11-06 poster-DYSCO/poster.tex
Poster for DYSCO

\title{Simple connectome inference from partial correlation statistics in calcium imaging}
\author{Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu, Gilles Louppe, Damien Ernst and Pierre Geurts\\[1.5ex]
{\tiny
\includegraphics[scale=0.16]{images/mail.png}~\url{a.sutera@ulg.ac.be}
%\includegraphics[scale=0.6]{images/twitter.png}~\href{https://twitter.com/glouppe}{@glouppe}
\includegraphics[scale=0.18]{images/github.png}~Code source available at \url{https://github.com/asutera/kaggle-connectomics}
}}

@@

\scalebox{2}{\includegraphics{poster-pics.pdf}}
{    \begin{pspicture}(20,20)

 	   \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](2,3)(1.8,2.8)
 	   \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](8.3,3)(1.5,2.8)

@@

		% text
		\rput(5.35,3.3){$p_{i,j}$}
		\rput(5.35,2.3){{$_{\textit{partial correlation}}$}}
		\rput(5.35,1.9){{$_=$}}
		\rput(5.35,1.5){{$_{\textit{degree of association}}$}}
		\rput(5.3,1.1){{$_{\textit{between neurons i and j}}$}}

		\rput(4.2,5){{\color{lightgreen} \textbf{known}}}

		\rput(6.3,0.6){{\color{lightgreen} \textbf{known}}}

@@

% \begin{textblock}{1}(0.01,0.99)
% {\fontsize{12}{10}\textbf{Acknowledgments:}}
% {\fontsize{8}{10}\textbf{A. Joly and G. Louppe are research fellows of the FNRS, Belgium. A. Sutera is a
% recipient of an FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
% PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
% Office.}}
% \end{textblock}

>>>>

\title{Simple connectome inference from partial correlation statistics in calcium imaging}
\author{Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu, Gilles Louppe, Damien Ernst and Pierre Geurts\\[1ex]
{\tiny
\includegraphics[scale=0.16]{images/mail.png}~\url{a.sutera@ulg.ac.be}
%\includegraphics[scale=0.6]{images/twitter.png}~\href{https://twitter.com/glouppe}{@glouppe}
\includegraphics[scale=0.18]{images/github.png}~Code source available at \url{https://github.com/asutera/kaggle-connectomics}\\[1ex] This paper presents research results of the Belgian Network DYSCO (Dynamical Systems, Control, and Optimization), funded by the Interuniversity Attraction Poles Programme initiated by the Belgian Science Policy Office.}}

@@

\scalebox{2}{\includegraphics{network_poster.pdf}}
{    \begin{pspicture}(20,20)

 	   % \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](2,3)(1.8,2.8)
 	   % \psellipse[fillstyle=solid,linewidth=2pt,linecolor=lightgreen,linestyle=dashed,fillcolor=lightgreen!10](8.3,3)(1.5,2.8)

@@

		\rput(4.5,3){{\color{lightblue} \textbf{i}}}
		\rput(6.2,3){{\color{lightblue}  \textbf{j}}}

		% text
		% \rput(5.35,3.3){$p_{i,j}$}
		% \rput(5.35,2.3){{$_{\textit{partial correlation}}$}}
		% \rput(5.35,1.9){{$_=$}}
		% \rput(5.35,1.5){{$_{\textit{degree of association}}$}}
		% \rput(5.3,1.1){{$_{\textit{between neurons i and j}}$}}

		% \rput(4.2,5){{\color{lightgreen} \textbf{known}}}

		% \rput(6.3,0.6){{\color{lightgreen} \textbf{known}}}

@@
